### 2023-02-13 article.tex
Fix conclusion

When applying these general recomendations to code, 
this list can be phrased more precisely:
code should be comprehensive in supplying 
automatically generated metadata (such as commit history and code coverage).
The documentation should be as extensive as recommended by the 
software development literature and have co-evolved with the
code following the best practices in literate programming. 
To be computer friendly,
code should be able to run on at least one independent entity,
such as a GitHub Actions server or from a Singularity container.

The second step for code to be useful paradata is to add CI, 
to stand the test of time better.
The ultimate step is to publish code in a container.

@@

When research truly needs to be reproducible, putting the code 
of an experiment into a container is a good solution, as it 
can stand the test of time better.
Creating such a container, however, requires more skill
that -as of today- is not rewarded,
partly as containers follow FAIR data principles only poorly.
However, such runnable code is the current pinnacle of reproducible research.

@@

The simplest and most impactful step to make code more useful paradata
is, however, to publish it on a code hosting website 
along a publication. From then on, the next steps can be taken 
gradually as the skills of the author(s) progress.
To quote \cite{barnes2010publish}: Publish your code, it is good enough.

>>>>

When applying these general recomendations to code, 
this list can be phrased more precisely:

\begin{enumerate}
  \item Code should be comprehensive 
    in supplying automatically generated metadata (such as commit history and code coverage).
  \item The documentation should be as extensive as recommended by the 
    software development literature.
  \item The documentation should have co-evolved with the
    code following the best practices in literate programming. 
  \item Code should be made machine-readable by, at least,
    being uploaded to a code hosting website.
    Ideally, the code is checked by CI and is put in a container.
\end{enumerate}

For the preservation of code, these are the recommendations:

\begin{enumerate}
  \item Uploading code to a code hosting website is better than
    not publishing code at all.
  \item Adding CI to code allows one to detect the day when that code 
    does not run anymore.
  \item Putting the code in a container is the best way to preserve code.
\end{enumerate}

@@

When research truly needs to be reproducible, putting the code 
of an experiment into a container is today's best solution,
as containers are the best solution to keep code running for the longest 
amount of time.
Creating such a container, however, requires more skill
that -as of today- is not rewarded,
although an experiment put into a container 
can be considered the pinnacle of reproducible research.

@@

The simplest and most impactful step to make code more useful paradata
is, however, to publish it on a code hosting website 
along a publication. From then on, the next steps can be taken 
gradually as the skills of the author(s) progress.
To quote: Publish your code, it is good enough \cite{barnes2010publish}.
